---
title: "R Notebook"
output: html_notebook
---

### This notebook conducts an experiment to induce det to det correlation and week to week corr in RCP17 data.

```{r}

source("helper_functions.R")


# code block to import det to det correlations and getting them into matrix form.
raw_corr_file_names <- list.files(path = str_c(getwd(), "/RCP17data/RCP17_detector_spearman_correlations")) #get the correlation file names in the data folder
corr_months <- str_split(raw_corr_file_names, "_") %>% sapply(function (x) x[1]) %>% unique #extracting month names from file names

  det_to_det_train_corr_leave_list <- list()
  det_to_det_train_corr_noleave_list <- list()
  #loop for reading in the correlation files of leave and no leave group and making positive definite correlation matrices of them
  for (month in corr_months){
    corr_vect <- suppressMessages(read_csv(str_c(getwd(), "/RCP17data/RCP17_detector_spearman_correlations/", month, "_Correlations_Leave.csv")))$`Spearman Correlation` %>% as.numeric
    det_to_det_corr <- vec2symmat(invec = corr_vect)
    det_to_det_corr <- round(det_to_det_corr, 10)
    det_to_det_corr[is.na(det_to_det_corr)] <- 0
    print(isSymmetric(det_to_det_corr))
    print(is.positive.definite(det_to_det_corr))
    if (is.positive.definite(det_to_det_corr) == FALSE){
      det_to_det_corr <- nearPD(det_to_det_corr) %>% .$mat %>% as.matrix
      diag(det_to_det_corr) <- 1
    }
    print(is.positive.definite(det_to_det_corr))
    det_to_det_train_corr_leave_list[[month]] <- det_to_det_corr
    
    
    corr_vect <- suppressMessages(read_csv(str_c(getwd(), "/RCP17data/RCP17_detector_spearman_correlations/", month, "_Correlations_NoLeave.csv")))$`Spearman Correlation` %>% as.numeric
    det_to_det_corr <- vec2symmat(invec = corr_vect)
    det_to_det_corr <- round(det_to_det_corr, 10)
    det_to_det_corr[is.na(det_to_det_corr)] <- 0
    print(isSymmetric(det_to_det_corr))
    print(is.positive.definite(det_to_det_corr))
    if (is.positive.definite(det_to_det_corr) == FALSE){
      det_to_det_corr <- nearPD(det_to_det_corr) %>% .$mat %>% as.matrix
      diag(det_to_det_corr) <- 1
    }
    print(is.positive.definite(det_to_det_corr))
    det_to_det_train_corr_noleave_list[[month]] <- det_to_det_corr
    
  } # end of correlations loop

det_train_corr_noleave_chol_decomp_list <- lapply(det_to_det_train_corr_noleave_list, chol)
det_train_corr_leave_chol_decomp_list <- lapply(det_to_det_train_corr_leave_list, chol)
  
```

```{r}
all_detectors <- c("001a","002a","002b","002c","002d","003a","004a","004b","004c","004d","005a","006a","006b","006c","006d","007a","008a","008b","008c","008d","009a","010a","011a","011b")
time_corr_mat <- suppressMessages(read_csv(str_c(getwd(), "/RCP17data/RCP17_time_spearman_correlations/Time_Correlations_Spearman.csv"), skip = 1, col_names = F))
time_corr_mat[,1] <- NULL #drop first column
time_corr_train_list <- list()
row_counter <- 0
  #loop for reading in the correlation file of time to time correlation and making positive definite correlation matrices of each of the detectors
  for (det in all_detectors){
    row_counter <- row_counter+1
    time_corr <- vec2symmat(invec = as.numeric(time_corr_mat[row_counter,]))
    time_corr <- round(time_corr, 10)
    time_corr[is.na(time_corr)] <- 0
    print(isSymmetric(time_corr))
    print(is.positive.definite(time_corr))
    if (is.positive.definite(time_corr) == FALSE){
      time_corr <- nearPD(time_corr) %>% .$mat %>% as.matrix
      diag(time_corr) <- 1
    }
    print(is.positive.definite(time_corr))
    time_corr_train_list[[det]] <- time_corr
    
  } # end of correlations loop

train_time_corr_chol_decomp_list <- lapply(time_corr_train_list, chol)

```

```{r}
number_of_people_in_org <- as.integer(lapply(list_of_all_detector_samples_noleave_train, nrow))+as.integer(lapply(list_of_all_detector_samples_leave_train, nrow))
highest_num_of_people <- sort(number_of_people_in_org, decreasing = T)[1]
gaussian_iids_list <- list()
for (det in all_detectors){
  temp_list <- list()
  for (m in 1:length(given_months)){
    temp_list[[m]] <- rnorm(n = highest_num_of_people) %>% as.data.frame
  }
gaussian_iids_list[[det]] <- bind_cols(temp_list) %>% as.matrix #gaussian iids for one detector across given months
}

time_correlated_gauss_samples_list <- lapply(1:total_num_detectors,function(i,m,v){m[[i]]%*%v[[i]]},m=gaussian_iids_list,v=train_time_corr_chol_decomp_list)




```


### Check the pattern of correlation between detectors across months
```{r}
detector_to_check <- 2
for (det in 1:total_num_detectors){

corr_of_dets_over_time <- lapply(1:length(given_months), function(i,l,d1,d2){l[[i]][d1,d2]}, l=, d1=detector_to_check, d2=det) %>% as.numeric #change value of d1 and d2 to change the detectors

plot(corr_of_dets_over_time, ylim=c(-1,1), type="l")

}
print(all_detectors[detector_to_check])

```

```{r}
det_to_det_train_corr_noleave_list[["2015-11"]] %>% View
```

### use the existing detector correlated data generated from RCP17_Model_12-20.R and following code induces time to time correlations.
```{r}
all_months_pop_1 <- read_csv("populations/all_months_pop_1.csv")
train_pop_data <- all_months_pop_1 %>% filter(month %in% given_months)

train_pop_list <- split(train_pop_data , f = train_pop_data$month)
#train_pop_list <- lapply(train_pop_list, function(df){subset(df, select=-c(uid,label,month))})
pop_sizes <- lapply(train_pop_list, function(df){nrow(df)}) %>% as.numeric
avg_pop_size <- mean(pop_sizes) %>% round
#loop to over-sample and under-sample populations to hav equal length populations across months
for (item in names(train_pop_list)){
  if (nrow(train_pop_list[[item]]) < avg_pop_size)
  {
    num_rows <- avg_pop_size - nrow(train_pop_list[[item]])
    train_pop_list[[item]] <- bind_rows(train_pop_list[[item]], train_pop_list[[item]][sample(num_rows),])
  } else {
    num_rows <- avg_pop_size
    train_pop_list[[item]] <- train_pop_list[[item]][sample(num_rows),]
  }
}
detector_monthly_dists_list <- list()
dist_list <- list()
counter <- 3
for (det in all_detectors){
  counter <- counter+1
  for (month in names(train_pop_list)){
  dist_list[[month]] <- train_pop_list[[month]][,counter]
  }
  detector_monthly_dists_list[[det]] <- bind_cols(dist_list)
}

```

# correlate the data over months

```{r}
  copula_time_corr_samples_list <- list()
  time_correlated_train_list <- list()
  counter <- 0
  for (det in names(detector_monthly_dists_list)){
    counter <- counter+1
    #copula samples generating for eight months
    norm_cop_obj <- normalCopula(param = as.numeric(time_corr_mat[counter,]), dispstr = "un", dim = length(given_months)) # create gaussian copula oject
    copula_time_corr_samples_list[[det]] <- data.frame(rCopula(copula = norm_cop_obj , n = nrow(as.data.frame(detector_monthly_dists_list[[det]])))) #sample from copula object
    
    
    #correlating the training data across eight months
    time_correlated_train_list[[det]] <- CorrelateData(DetectorData = as.data.frame(detector_monthly_dists_list[[det]]), CopulaMatrix = as.data.frame(copula_time_corr_samples_list[[det]]))
}
```


### test time correlated data
```{r}

cor(time_correlated_train_list[["011b"]]) # data passes the test of monthly correlation

```

### now retransforming time correlated data back to original format

```{r}
time_correlated_pop_list <- list()
counter <- 0
for (month in given_months){
counter <- counter+1
time_correlated_pop_list[[month]] <- lapply(time_correlated_train_list, function(df,month){df[,month]}, month = counter) %>% bind_cols
time_correlated_pop_list[[month]] <- bind_cols(train_pop_list[[month]][,c("uid","label","month")], time_correlated_pop_list[[month]])
}
```

# calculating the average detector to detector correlation across months

```{r}



```

